My Statistics 3494W Proposal

### 2022-10-05 Proposal/Proposal.tex
commit #Discussion

>>>>

\section*{Discussion}
I expect to see in an increase in calls during the early afternoon. This is typically when people have a lunch break and would have 
easy access to call the call center. There may be in increase in the early evening after people get out of work. In regards to agent
performance, I feel that most agents will be relatively consistent in regards to number of calls, wait time, and other factors. I believe 
this finanical firm would have the best of the best working for them. Because I have data from 2020, that may skew the data due to the impacts
of COVID-19. My impacts will allow this finanical firm to optimize their call center and have a more efficient and effective process. They will
also have a better expectation of what will happen after something unexpected occurs, like a website outage. If my investigation is not what I 
expect, I believe that would be okay because this would give a different prospectives of when and why people call. I believe the more prospective
the more efficient the call center can be. My findings have the ability to both challenge and corroborate assumptions when it comes to the best way to 
forecast call center data depending on my conclusions.
